The \dealii Library, Version 9.6

### 2024-09-24 9.6/paper.tex
Briefly describe the hanging node support for Nedelec_SZ.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item \dealii{} now requires and makes use of the C++17 language standard.
  \item We have continued to make progress in supporting simplex and
    mixed meshes -- mesh types that \dealii{} has traditionally not
    supported at all. Specifically, the current release uses
    better strategies for refinement of tetrahedra that result in
    better-shaped child cells. It also contains
    support for cubic finite elements on simplices.
  \item The \texttt{FE\_NedelecSZ} class that contains our
    implementation of the N\'ed\'elec element using the orientation
    scheme of \cite{Zag06} now supports the computation of hanging
    node constraints for locally refined meshes.
    \todo[inline]{Sebastian: Is there anything more to say here, maybe some reference? If
      you want, we can also list this point in the list above, and add
      a whole section 2.x for it. If you think there is nothing more
      that needs to be said, just delete this note.}
  \item The \texttt{AffineConstraints} class stores and processes
    constraints on degrees of freedom in \dealii{}. Such constraints
    can be of the (homogeneous) form $x_3 = \frac 12 x_{14} + \frac 12 x_{15}$ as is
    common when using hanging node constraints (here, $x_3$ could
    represent the value of the solution at a hanging node, and $x_{14}$
    and $x_{15}$ are the values of the two adjacent degrees of freedom on
    the parent edge that contains the hanging node); or they can be of
    the form $x_{12}=42$ as is common when using Dirichlet boundary
    the (inhomogeneous) form $x_{12}=42$ as is common when using Dirichlet boundary
    conditions.

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item \dealii{} now requires and makes use of the C++17 language standard.
  \item We have continued to make progress in supporting simplex and
    mixed meshes -- mesh types that \dealii{} has traditionally not
    supported at all. Specifically, the current release uses
    better strategies for refinement of tetrahedra that result in
    better-shaped child cells. It also contains
    support for cubic finite elements on simplices.
   \item The \texttt{FE\_NedelecSZ} class that contains our 
    implementation of the N\'ed\'elec element using the orientation 
    scheme of \cite{Zag06} now supports the computation of hanging 
    node constraints for locally refined meshes. 
    Therefore, the sign-conflict that arises for hp quadrilateral and 
    hexahedral N\'ed\'elec elements in the presence of hanging edges 
    and hanging faces was addressed for the implementation details; 
    we refer to \cite{Kinnewig2024}. 
    The \texttt{FE\_NedelecSZ} class and the hanging node constraints 
    automatically account for the presence of hanging edges and hanging 
    faces; therefore, there is no difference for the user when using 
    \texttt{FE\_NedelecSZ} as finite elements compared to other finite 
    element classes when used on triangulations with hanging nodes. 
    Note that the special case where, in 3D, more than four cells with 
    different refinement levels share a common edge is not covered yet.
  \item The \texttt{AffineConstraints} class stores and processes
    constraints on degrees of freedom in \dealii{}. Such constraints
    can be of the (homogeneous) form $x_3 = \frac 12 x_{14} + \frac 12 x_{15}$ as is
    common when using hanging node constraints (here, $x_3$ could
    represent the value of the solution at a hanging node, and $x_{14}$
    and $x_{15}$ are the values of the two adjacent degrees of freedom on
    the parent edge that contains the hanging node); or they can be of
    the form $x_{12}=42$ as is common when using Dirichlet boundary
    the (inhomogeneous) form $x_{12}=42$ as is common when using Dirichlet boundary
    conditions.
